### 2014-03-01 paper/real.tex
Wip

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains reference.
%
Hence, as discussed in Section~\ref{sec:concrete} we restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects~\tocite{}.
%
In our formalization this amounts to restricting the IFC language rule
for |send| as follows:
  \Red{HERE: typeof!!!}

Indeed this coarse-grained approach is already used by browsers in the
Worker API~\tocite{}, which provides client-side JS with primitives
for executing code in a separate thread, called a Worker.
%
Each Worker has a separate runtime with a fresh global object.
%
In turn, exchanging information between runtimes is accomplished with
message-passing, i.e., \texttt{postMessage}.
%
The message-passing approach is, in part, due to ECMAScript's lack
of well-defined semantics for concurrency.
%
Hence sharing and accessing objects such as the DOM across threads is
undefined.
%

>>>>

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains reference.
%
Hence, as discussed in Section~\ref{sec:concrete} we restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects~\tocite{}.
%
In our formalization this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie') , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' ie)), ldots)
.->
iS'; sched S (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and Worker
communications~\tocite{}.
%
Insomuch, that the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the Worker JS object~\tocite{}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across Worker
  threads is undefined.
}

\Red{HERE}
Our |specLangJS roundrobinf| implementation builds on the existing
Worker implementat
